# Results

```{r}
#This is how to load json files 
library(jsonlite)
library(tidyverse)
#pca libraries conflict with dplyr

grenades <- jsonlite::fromJSON("data/ALL_grenades.json", simplifyVector = TRUE)
kills <- jsonlite::fromJSON("data/ALL_kills.json", simplifyVector = TRUE)
damages <- jsonlite::fromJSON("data/ALL_damages.json", simplifyVector = TRUE)
flashes <- jsonlite::fromJSON("data/ALL_flashes.json", simplifyVector = TRUE)
```




```{r}
#This is wheree we store the final score of each match
wins <- kills %>% group_by(match_id) %>% summarise(round_tot=last(round_tot)+1,team1=last(match_team1),team2=last(match_team2),winner=last(round_won_by),looser=if_else(last(round_won_by)!=last(match_team1),last(match_team1),last(team2)))

#final score formula takes into account overtime. An overtime can last up to 6 rounds before another overtime occurs

wins <- wins %>%  mutate(final_score_winner=if_else(round_tot<31,16, 19+3*(  (round_tot-31)%/%6))) %>%  mutate(final_score_looser=round_tot-final_score_winner) %>% mutate(score_diff=(final_score_winner-final_score_looser)/round_tot)

```


## Evaluate the performance of teams and players with a new rating

We are going to see how commonly used indicators impacts the final score.

We generated standard indicators used by event organisors and sites from the datasets:

- kpr : average number of kills per round

- adr: average damage per round

- first_kill_ratio: ratio of the time where the team or player gets the first kill (which grants a numerical advantage)

- smokes_per_round: average number of smokes thrown in a round

- assist_ratio: ratio of kills assisted by another player than dealt more than 40 points of damage

- non_traded_ratio: ratio of kills where the victim team could not get a revenge to prevent a numerical advantage

- avg_flash_duration: average time of blinded enemy players caused by flash grenades

- blinded_ratio: ratio of kills where the victim was blinded by a flash grenade

- strafing: ratio of kills where the attacker was strafing i.e. was side stepping to avoid being immobile to the opposing player

- hs_ratio: ratio of kills where the attackerclanded a shot in the enemy's head, resulting in more damage points

```{r fig.width=8}

#team stats on kills
team_kills <- kills %>% filter(attackerTeam!=victimTeam) %>%  group_by(match_id,attackerTeam) %>% summarise(kills_tot=n(),kpr=n()/last(round_tot),team=last(attackerTeam),hs_ratio= sum(isHeadshot==TRUE)/n(),blinded_ratio=sum(victimBlinded==TRUE)/n(),first_kill_ratio=sum(isFirstKill==TRUE)/last(round_tot),non_traded_ratio=sum(isTrade==FALSE)/n(),assist_ratio= sum(!is.na(assisterTeam))/last(round_tot))



#team stats on  damages
team_damages <- damages %>% filter(attackerTeam!=victimTeam) %>%  group_by(match_id,attackerTeam) %>% summarise(adr=sum(hpDamageTaken)/last(round_tot),team=last(attackerTeam),strafing=sum(attackerStrafe==TRUE)/n())

#team stat on flash 

team_flashes <- flashes %>% filter(attackerTeam!=playerTeam) %>%  group_by(match_id,attackerTeam) %>% summarise(avg_flash_duration=sum(flashDuration)/last(round_tot),team=last(attackerTeam))

#team stats for grenades
team_grenades <- grenades  %>% rename(attackerTeam=throwerTeam) %>%   group_by(match_id,attackerTeam) %>% summarise(grenades_per_round=n()/last(round_tot),team=last(attackerTeam),smokes_per_round=sum("Smoke Grenade"==grenadeType)/last(round_tot),attack_grenades_round=sum("Smoke Grenade"!=grenadeType)/last(round_tot),event=last(match_event))

#join everything
team_killsstat <- inner_join(team_kills,wins) %>% inner_join(team_damages) %>% inner_join(team_flashes) %>%  inner_join(team_grenades)  


#create y axis score difference data
team_killsstat <- team_killsstat %>% mutate(relative_score_diff=if_else(winner!=attackerTeam,-score_diff,score_diff))



library(reshape2)
library(forcats)
#melt for graph display
df.mlt <- melt(team_killsstat,  variable.name="var",id.vars=c("relative_score_diff","score_diff","match_id","attackerTeam","kills_tot","team","winner","looser","final_score_winner","final_score_looser","team1","team2","round_tot","event"))
df.mlt <- df.mlt %>% mutate(yvalue=as.double(value)) 
#add correlation tests
df.mlt <-  df.mlt %>% group_by(var) %>% 
    mutate(pvalue= cor(yvalue, relative_score_diff)) %>% ungroup() %>% mutate(label_names=paste(as.character(var),strtrim(as.character(pvalue), 5)), sep = " ", collapse = NULL) %>% mutate(label_names=fct_reorder(label_names, -pvalue))


mylabeller <- function(variable,value){
  return(cor_tests[value])
}

#facetted graph with facets ordered by correlation test

df.mlt %>% ggplot(aes(x=yvalue, y=relative_score_diff))+
  #geom_smooth(method = "lm", se = FALSE) +
  geom_point(size = .15,alpha=0.3) +
  geom_smooth(method='lm', formula = y~x, colour='red',alpha=0.5)+
  #geom_text(, aes(x = 3, y = 0, label = paste(" ",pvalue), family = "serif"), color = 'blue',  parse = TRUE)+
  facet_wrap(~label_names, scales = "free") +
  xlab("Team stat") +
  ylab("relative score diff") +
  ylim(-2, 4)+
  labs(title = "Scatter plot of the relative score difference depending on indicator values, \nwith correlation test score", x = "Indicator value",  y = "Relative score difference")+
  theme_linedraw()



```

We can see that some indicators are more correlated than others to the relative score difference (difference of the winner's and loser's scores over the sum of the scores). 
For instance the kpr indicator has a correlation score of 0.6 with the relative score difference and thus can be used to evaluate a player's performance. 
On the contrary, the strafing and hs_ratio indicators have little to do with a team's success. Overall we can see that kpr (ie:average number of kills per round),
adr (ie: average damage per round) and first_kill_ratio are three indicator variables which has a strong positive correlation with relative score difference


A PCA analysis better helps visualize indicators that better reflects a team's chance of winning.

```{r }
#uncomment to install ggbiplot for PCA

#library(cli)
#library(devtools)

#install_github("vqv/ggbiplot")
```

```{r}
pca.variables <- c('kills_tot', 'kpr', 'hs_ratio', 'blinded_ratio', 'first_kill_ratio',
'non_traded_ratio', 'assist_ratio', 'strafing', 'adr',  'avg_flash_duration', 'grenades_per_round')

team_killsstat.pca <- prcomp(team_killsstat[,pca.variables], center = TRUE,scale. = TRUE)

#summary(team_killsstat.pca)
team_killsstat <- team_killsstat %>% mutate(won=if_else(relative_score_diff>0,TRUE,FALSE))
```

```{r pca, fig.height=8}
library(ggbiplot)
ggbiplot(team_killsstat.pca , obs.scale = 1, var.scale =1,circle=TRUE, group=team_killsstat$won,varname.adjust = 1.7, varname.size = 2.3,  alpha = 0.2)+ xlim(-4.5, 3) + 
  ylim(-3.1, 5) +
  ggtitle("PCA of team statistics in matches")  +
  theme(plot.title = element_text(hjust = 0.5))+
  labs(colour = "Match won")

```

Indicators with directions opposite to the loosing matches and closer to the correlation circle are the most interesting ones. As we can see, the PCA analysis confirms the findings with the correlation tests. It also tells us that many of these indicators are themselves correlated since the angle between their arrows is very small: the principal components were not able to separate these features in the reduced space.



Note that there is no indicator with a strong correlation (more than 0.7) with the score difference. But combining those indicators can still lead to a better overall rating score. We are going to achieve it with a multi-variable linear regression.

```{r rating}


# new stat generation with the linear regression lm

fit <- lm(relative_score_diff ~ kpr + adr + first_kill_ratio + grenades_per_round + attack_grenades_round + smokes_per_round + assist_ratio + non_traded_ratio + avg_flash_duration, data=team_killsstat)



coef <- coefficients(fit)

#new combined rating, with the coefficients. Start at 0.
team_killsstat <- team_killsstat %>% mutate(rating=100*(coef[1]+kpr*coef[2]+adr*coef[3]+first_kill_ratio*coef[4]+grenades_per_round *coef[5]+attack_grenades_round*coef[6]+assist_ratio*coef[8]+non_traded_ratio*coef[9]+avg_flash_duration *coef[10])) %>%  mutate(rating=100*(rating-min(rating))/(max(rating)-min(rating)))

coef

```

## Teams performance

With a new combined rating, we can take a closer look at each team's performance relative to each other

```{r  teamrating , fig.height=8,  fig.width=10}
# TOP TEAMS AT EACH EVENT
#filtering
top_teams <- team_killsstat %>% group_by(team,event) %>% summarize(rating=mean(rating)) %>% filter( !is.nan(rating) ,rating!=0) 
#list of events
level_order <- c('DreamHack Winter 2013','EMS One Katowice 2014','ESL One Cologne 2014','DreamHack Winter 2014','ESL One Katowice 2015','ESL One Cologne 2015','DreamHack Open Cluj-Napoca 2015','MLG Columbus 2016','ESL One Cologne 2016','ELEAGUE Major 2017','PGL Major Krakow 2017','ELEAGUE Major 2018','FACEIT Major 2018','IEM Katowice 2019','StarLadder Major Berlin 2019')

# generate winner col to display winner of each event
top_teams <- top_teams %>% mutate(winner= (team=="Fnatic" & event=="ESL One Cologne 2015")| (team=="Team EnVyUs" & event=="DreamHack Open Cluj-Napoca 2015") |  (team=="Luminosity Gaming" & event=="MLG Columbus 2016") | (team=="SK Gaming" & event=="ESL One Cologne 2016") | (team=="Gambit Gaming" & event=="PGL Major Krakow 2017") |(team=="Cloud9" & event=="ELEAGUE Major 2018") | ((team=='Astralis')&(event %in% c("StarLadder Major Berlin 2019","FACEIT Major 2018","IEM Katowice 2019","ELEAGUE Major 2017"))))


# reordering  function inside facets
reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
  new_x <- paste(x, within, sep = sep)
  stats::reorder(new_x, by, FUN = fun)
}

# reordering  function inside facets
scale_x_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
}


ggplot(data=top_teams, aes(x=reorder_within(team,-rating,event), y=rating,fill=winner)) +
facet_wrap(~factor(event,levels=level_order), scales = "free") +
scale_x_reordered() +
ggtitle("Team ratings at each event")  +
geom_bar(stat="identity")+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

As expected the winner team is consistently in the top team ratings. 6 times out of 10, the winner team has the best rating between 70 and 100. However sometimes, some teams get even better ratings than the winner. This is explained by the fact that some teams have a solid performance throughout the tournament, only to get eliminated in the final stage. For example, in the Eleague Major 2017 event, Virtus.Pro was eliminated by Astralis in the finals, and Faze Clan got eliminated in the quarter-finals. [1]

## Players performance

Events and websites like HLTV generally focus on players's performance on individual events. However it would be interesting to look at a player's performance across all event. This would smooth out players that had unexpectedly good or bad performance in an event. 

```{r playerrating}
#all time player stats
player_kills <- kills %>% filter(attackerTeam!=victimTeam) %>%  group_by(match_id,attackerSteamID) %>% summarise(kills_tot=n(),kpr=n()/last(round_tot),team=last(attackerTeam),hs_percent= sum(isHeadshot==TRUE)/n(),blinded_percent=sum(attackerBlinded==TRUE)/n(),blinded_percent=sum(victimBlinded==TRUE)/n(),first_kill_percent=sum(isFirstKill==TRUE)/last(round_tot),first_kill_percent=sum(isFirstKill==TRUE)/last(round_tot),non_traded_percent=sum(isTrade==FALSE)/n(),assist_percent= sum(!is.na(assisterTeam))/last(round_tot))

#player stats on  damages
player_damages <- damages %>% filter(attackerTeam!=victimTeam) %>%  group_by(match_id,attackerSteamID) %>% summarise(adr=sum(hpDamageTaken)/last(round_tot),team=last(attackerTeam),strafing=sum(attackerStrafe==TRUE)/n())

#player stat on flash 

player_flashes <- flashes %>% filter(attackerTeam!=playerTeam) %>%  group_by(match_id,attackerSteamID) %>% summarise(avg_flash_duration=sum(flashDuration)/last(round_tot),team=last(attackerTeam))

#player stats for grenades

player_grenades <- grenades  %>% rename(attackerSteamID=throwerSteamID) %>%   group_by(match_id,attackerSteamID) %>% summarise(grenades_per_round=n()/last(round_tot),smokes_per_round=sum("Smoke Grenade"==grenadeType)/last(round_tot),attack_grenades_round=sum("Smoke Grenade"!=grenadeType)/last(round_tot),name=last(throwerName),event=last(match_event),date=last(match_date))

#join everything
playerstat <- player_kills %>% inner_join(player_damages) %>% inner_join(player_flashes) %>%  inner_join(player_grenades)  %>% mutate(rating=100*(coef[1]+kpr*coef[2]+adr*coef[3]+first_kill_percent*coef[4]+grenades_per_round *coef[5]+attack_grenades_round*coef[6]+assist_percent*coef[8]+non_traded_percent*coef[9]+avg_flash_duration *coef[10]))


playerstat <- playerstat %>% mutate(rating=100*(rating-min(rating))/(max(rating)-min(rating)))




playerstat <- playerstat %>%  filter(!is.na(rating)) %>% group_by(attackerSteamID) %>%  summarize(name=last(name),rating=mean(rating),match_played=n())

  
```
```{r topplayers}
B <- playerstat %>%  filter(match_played>10) %>% top_n(30,rating) %>% arrange(rating) %>% mutate(name = factor(name, levels = .$name))   %>% ggplot(., aes(rating, name))  +
        geom_point()+
  labs(title = "Top 30 players all time", x = "Rating",  y = "Name")

A <- playerstat  %>%  filter(match_played>10)  %>%  top_n(-30,rating) %>% arrange(rating) %>% mutate(name = factor(name, levels = .$name)) %>% ggplot(., aes(rating, name)) + 
        geom_point()+
  labs(title = "Worst 30 players of all time", x = "Rating",  y = "Name")

library(patchwork)
A+B
```

The player Autimatic has the highest rating of all, and has one win with his team Cloud9 in the Boston Major. Interestingly, Zywoo, s1mple and device are the immediate 3 highest rated players after autimatic. The fact that those three players where nominated in the top 3 players in 2018 and 2019 by the [HLTV](https://hltv.org) website means that our combined rating reflects the different ratings of other sites such as HLTV. Note that the player Zywoo started his career during 2018 thus is not this the top player raking of this year. [2], [3], [4]

There is almost 20 points of rating score  difference between the top rated player and the 30th best rated player. The same can the said for the worst rated player. As a result, it is quite easy to differentiate players as the ratings are not too close to each other.

The rating is derived from the combined effort of the player considering various parameteres like avergae kills per round, damages through grenade, head shot etc, number of first kill shot , health of the player, number of flashes etc.It is often hard to compare teams and players across events because players often change teams.
One way to cross the information is to visualize the teams of a player:

```{r interactalluv}
library(parcoords)

wins <- kills %>%  filter(attackerTeam!=victimTeam) %>%  group_by(match_id,round_num) %>% summarise(map=last(map_name),T_team=last(if_else(attackerSide=="T","T","CT")))
most_played <- kills %>%  
        group_by(match_id ) %>%
        summarise(attackerSteamID=last(attackerSteamID),attackerName=last(attackerName) ) %>%
        group_by(attackerSteamID) %>% 
        dplyr::summarise(match_count= n() , name=last(attackerName))
most_played <- most_played %>% top_n(15,match_count)
names <- most_played$name
players <- kills %>% group_by(match_event,attackerSteamID)   %>%  summarise(name=last(attackerName),team=last(attackerTeam),date=last(match_date),event=last(match_event) )
players <- filter(players, name %in% names)
players <- select(players , -c(attackerSteamID , event))
col_order <- c("name",
               "team","match_event") 
players <- players[, col_order]
players %>% 
  arrange(team) %>% 
  parcoords(rownames=F,color= list(
       colorBy = "name",
       colorScale='scaleOrdinal',
       colorScheme = "schemeCategory10"),
       withD3=T,brushMode="1D-axes",reorderable = T,queue=T,alpha=0.5)
```

This shows us, how players changed teams over the course of various events and how few players remained in the same team for multiple events.
For instance, players Flamie and Edward remained in the team Natus Vincere for multiple events.


```{r alluvial , fig.height=6,fig.width=13}

library(easyalluvial)

#conflict with mosaic
conflict_prefer("sum", "base")
conflict_prefer("cor", "base")

names <- c("device","dupreeh","Xyp9x","Magisk","gla1ve")

players <- kills %>% group_by(match_event,attackerSteamID)   %>%  summarise(name=last(attackerName),team=last(attackerTeam),date=last(match_date) )
players <- filter(players, name %in% names)

#players <- players %>% group_by(team,name) %>% summarise(name=last(name),team=last(team),date=last(date), count = n() , event = last(match_event),attackerSteamID=last(attackerSteamID))



level_order <- c('EMS One Katowice 2014','ESL One Cologne 2014','DreamHack Winter 2014','ESL One Katowice 2015','ESL One Cologne 2015','DreamHack Open Cluj-Napoca 2015','MLG Columbus 2016','ESL One Cologne 2016','ELEAGUE Major 2017','PGL Major Krakow 2017','ELEAGUE Major 2018','FACEIT Major 2018','IEM Katowice 2019','StarLadder Major Berlin 2019')
#players <- players[match(level_order, players$match_event),]
conflict_prefer("sum", "mosaic")
players <- players[order(factor(players$match_event, levels=unique(level_order))),]

alluvial_long(players
              , key = match_event
              , value = team
              , id = attackerSteamID
              , fill = name
              , fill_right = F
              , NA_label = 'None'
              ,order_levels_key =level_order
              ,col_vector_value = c("blue","black","green","yellow","red")
              )+labs(title = "Team changes",  y ="Player", x ="Event")
```
One of the most successful teams is Astralis with 3 Major wins. A core of 3 players (dupreeh, device, and Xyp9x) have been playing together for 10 events explaining the team's consistent success.




## Use in-game data to have the competitive advantage

The game data of matches is available to everyone and pro teams always watch their opponent's previous games to come up with strategies.

However, watching games takes time and some parts of this process can be automated. 

Even though it does not give information such as a team's reactions to specific events, 2d-density maps can give the general trends, and habits of a team or player.

For instance, one of the hardest player to play against is s1mple, especially with the AWP weapon because of its range. Parsing the game data allows to know where players can expect s1mple to be and where he can be aiming at with his weapon.  

```{r densitymap , fig.height=8, fig.height=10}
#heatmpas



library(ggpubr)
library(jpeg)

img <- readJPEG("img/de_mirage_light.jpg")



heat_kills <- damages %>%  filter(map_name == "de_mirage" ) %>% filter(attackerSteamID==76561198034202275) %>% filter(weapon=="AWP") %>% filter(attackerSide =="CT")
# Area + contour
a <- ggplot(heat_kills, aes(x=attackerX, y=attackerY) )+
background_image(img) +
#geom_point(alpha=0.2,color="red")+
stat_density_2d(aes(fill = log10(..level..)), geom = "polygon",alpha=0.6,h=294.1)+ scale_fill_continuous(type = "viridis")+
  geom_segment(aes(xend=victimX, yend=victimY),alpha=0.2)+
  xlim(-3050, 1700)+
  ylim(-3200,1520) + theme(aspect.ratio=1) +
  labs(title = "Positions of s1mple with the AWP weapon \non the map de_mirage, with \nbullet trajectories\nCT positions")+
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank())

b <- ggplot(heat_kills, aes(x=victimX, y=victimY) )+
background_image(img) +
#geom_point(alpha=0.2,color="red")+
stat_density_2d(aes(fill = log10(..level..)), geom = "polygon",alpha=0.6,h=294.1)+ scale_fill_continuous(type = "viridis")+
  geom_segment(aes(xend=attackerX, yend=attackerY),alpha=0.2)+
  xlim(-3050, 1700)+
  ylim(-3200,1520) + theme(aspect.ratio=1) +
  labs(title = "Positions of the victims hit by \ns1mple with AWP weapon \non the map de_mirage \nCT positions")+
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank())

a+b
```

Knowing the habits of a player and the positions where it is dangerous to be can avoid being surprised by the enemy and helps to come up with strategies to counter the enemy team. We can see in yellow where s1mple tends to be when he deals damage, and where the victim's positions are. The trajectories allow to link those two positions. We can see that s1mple often takes tight lines where the trajectory is tengeant to a corner of a wall.

## Game evolution and balance

People often attribute the success and longevity of the CSGO game to its balance, meaning that both teams have an equal chance of winning. However, this is difficult to achieve as it depends on multiple factors such as the weapon characteristics and map layout.

Because the developers have been continuously updating the maps and weapon characteristics, the probability to win a round on the T/CT sides has changed over the years.

```{r winrates}

wins <- kills %>%  filter(attackerTeam!=victimTeam) %>%  group_by(match_id,round_num) %>%  summarise(map=last(map_name),winner=last(round_won_by),T_team=last(if_else(attackerSide=="T",attackerTeam,victimTeam)),event=last(match_event),map=last(map_name))
wins <- wins %>% mutate(win_side=if_else(winner==T_team,'T','CT'))

global_wins <- wins %>% group_by(event) %>% summarise(event=last(event),tot=n(),T_percent=100*sum(win_side=='T')/n()) %>% mutate(CT_percent=100-T_percent)


level_order <- c('DreamHack Winter 2013','EMS One Katowice 2014','ESL One Cologne 2014','DreamHack Winter 2014','ESL One Katowice 2015','ESL One Cologne 2015','DreamHack Open Cluj-Napoca 2015','MLG Columbus 2016','ESL One Cologne 2016','ELEAGUE Major 2017','PGL Major Krakow 2017','ELEAGUE Major 2018','FACEIT Major 2018','IEM Katowice 2019','StarLadder Major Berlin 2019')


library(reshape2)
gloabl_wins_melt <- melt(global_wins,  variable.name="var",id.vars=c("event","tot"))

ggplot(gloabl_wins_melt, aes(x = factor(event, level = level_order), y = value, group=var, col=var))+ 
geom_line() + geom_point()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
labs(title = "Winrates for each event", x = "Events",  y = "Winrate (percentage)")+
labs(color='Side') 


```

The drop in the win percentage differences after 2016 can be attributed to the update of the nuke, inferno and overpass maps.
Maps updates often include changes in the layout to give more advantage to a given side.

```{r mapwinrates,  fig.height=8,fig.width=8}
map_wins <- wins %>% group_by(event,map) %>% summarise(event=last(event),tot=n(),T_percent=100*sum(win_side=='T')/n()) %>% mutate(CT_percent=100-T_percent)


map_wins_melt <- melt(map_wins,  variable.name="var",id.vars=c("event","tot","map"))

ggplot(map_wins_melt, aes(x = factor(event, level = level_order), y = value, group=var, col=var))+ 
facet_wrap(~map, ncol = 2)+
geom_line() + geom_point()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
labs(title = "Winrates for each map", x = "Events",  y = "Winrate (percentage)")+
labs(color='Side') 

```

In CS:GO, teams can play on a range of different map layouts in casual play and in professional tournaments. 
Anecdotally, players usually have a favourite map or one they think they preform poorly on. 
Professional teams often spend hours training on these maps, so it is interesting to see if winrate across different maps.


Nuke as been removed from the official maps after Katowice 2015 and reintroduced for Cologne 2016. [5] It was known to greatly favor the CT side, often forcing the team starting on the T side to have an impressive comeback after switching sides on the half time.
Of all maps, nuke had the worst balance especially during Dreamhack Winter 2014 with a *CT* win rate of 80%.


But after the nuke map update the balance greatly improved and the *CT* and *T* win rates were contained between 40% and 60%. In fact, in 2019 all maps where balanced with win rates between 40% and 60%, with de_inferno, de_dust2, de_nuke, and de_mirage being particularly balanced (win rates close to 50%). Overall, the Starladder Berlin Major 2019 event seems the most balanced Major ever. It is safe to say that game updates generally improved the balance of the game.
 
Note that the map pool changes for every event. The latest map being introduced is vertigo. Because it is a new map, it is not as balanced as the other ones. 


Weapons also impact the game balance.

```{r weaponusage , fig.height=10,fig.width=8}
level_order <- c('DreamHack Winter 2013','EMS One Katowice 2014','ESL One Cologne 2014','DreamHack Winter 2014','ESL One Katowice 2015','ESL One Cologne 2015','DreamHack Open Cluj-Napoca 2015','MLG Columbus 2016','ESL One Cologne 2016','ELEAGUE Major 2017','PGL Major Krakow 2017','ELEAGUE Major 2018','FACEIT Major 2018','IEM Katowice 2019','StarLadder Major Berlin 2019')


weapon_usage <- damages %>% group_by(match_id,attackerSteamID,weapon,round_num) %>% summarize(weapon=last(weapon),date=last(match_date),event=last(match_event),side=last(attackerSide),name=last(attackerName))


weapon_usage <- weapon_usage %>% group_by(event,weapon) %>% summarize(weapon=last(weapon),weapon_usage=n(),date=last(date),event=last(event),side=last(side))
#tot_count <- weapon_usage %>%  group_by(event) %>% summarize(tot_usage=sum(weapon_usage))
tot_count <- weapon_usage %>%  group_by(event) %>% summarize(tot_usage=sum(weapon_usage))
weapon_usage <- weapon_usage %>% inner_join(tot_count) %>%  mutate(weapon_percent=weapon_usage/tot_usage)


weapon_list <- c("UMP-45",'MAC-10','MP7','MP9','P90')
a <-  ggplot(weapon_usage %>% filter( (weapon %in% weapon_list)), aes(x = factor(event, level = level_order), y = weapon_percent, group=weapon, col=weapon))+ 
geom_line() + geom_point()+ theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
        labs(title = "Weapon usage\nsmg category",  y ="Weapon usage(%)")

weapon_list <- c("CZ75 Auto",'Desert Eagle','Five-SeveN','p250','Tec-9')
b <- ggplot(weapon_usage %>% filter( (weapon %in% weapon_list)), aes(x = factor(event, level = level_order), y = weapon_percent, group=weapon, col=weapon))+ 
geom_line() + geom_point()+ theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  labs(title = "Pistol category",  y ="Weapon usage(%)")

weapon_list <- c("AK-47",'SG 553','AUG','M4A4','M4A1')
c <- ggplot(weapon_usage %>% filter( (weapon %in% weapon_list)), aes(x = factor(event, level = level_order), y = weapon_percent, group=weapon, col=weapon))+ 
geom_line() + geom_point()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = "Rifle category",  y ="Weapon usage(%)",x="Events")




(a/b/c)



```

When the developers change a weapon's characteristic such as damage output, it can lead to a drop or spike in popularity.

For example, in 2017 developers tried to increase the usage of smg type weapons by increasing their damage output, especially for the ump. As a result, the ump was often used by teams when they could not get a rifle. But complains from pro players meant that the update was reverted. [6]

The same can be said for the cz-75 in 2018. Also, the p250, five-seven and tec-9 had their damage and accuracy decreased over the years and resulted in a drop in usages by the pro players.

Finally, it happens that players discover that a weapon can be very effective, even without its characteristics being changed. This is what happened in 2019 when players started to use the AUG and the SG 553 weapons for their good accuracy at long range. As a result, their effectiveness has been reduced in a later update. [7]


[1] Eleague Major 2017, Overview page, [HLTV.ORG](https://www.hltv.org/events/2471/eleague-major-2017)

[2] OFFICIAL: VITALITY UNVEIL TEAM, MIRAA, 2018[HLTV.ORG](https://www.hltv.org/news/25028/official-vitality-unveil-team)

[3] Top 20 players of 2019: INTRODUCTION, Striker, 2019 [HLTV.ORG](https://www.hltv.org/news/28749/top-20-players-of-2019-introduction)

[4] Top 20 players of 2018: INTRODUCTION, Professeur, 2018 [HLTV.ORG](https://www.hltv.org/news/25735/top-20-players-of-2018-introduction)

[5] NEW UPDATE ADDS NUKE TO ACTIVE DUTY, stich, 2016, [HLTV.ORG](https://www.hltv.org/news/17622/new-update-adds-nuke-to-active-duty)

[6] NEW UPDATE CHANGES THE UMP45, Sander, 2017, [HLTV.ORG](https://www.hltv.org/news/20546/new-update-changes-the-ump45)

[7] Release Notes for 4/10/2020, Valve, 2020, [update notes](https://blog.counter-strike.net/index.php/2020/04/29649/)

