---
title: "R Notebook"
output: html_notebook
---

## data lion drive link: https://drive.google.com/drive/folders/10wndQSJ15Pvd97XwZ32J_BSu3F-clxIQ?usp=sharing


##Useful info for all rows

"round_won_by": team that won the round
 "match_id": "0 astralis-vs-cr4zy-m1-inferno" unique match identifier
"map_name": name of map played
 "round_num": number of the round from 1 to the last round
"round_tot": total number of rounds in the match
"match_event": unique event identifier ex "StarLadder Major Berlin 2019"
"match_date": date of match in milliseconds
"match_team1": name of a team
"match_team2": name of the other team


## This is how to load json files

```{r}
#This is how to load json files 
library(jsonlite)
library(tidyverse)
grenades <- jsonlite::fromJSON("data/ALL_grenades.json", simplifyVector = TRUE)
kills <- jsonlite::fromJSON("data/ALL_kills.json", simplifyVector = TRUE)
damages <- jsonlite::fromJSON("data/ALL_damages.json", simplifyVector = TRUE)
flashes <- jsonlite::fromJSON("data/ALL_flashes.json", simplifyVector = TRUE)
```

```{r}
kills
wins <- kills %>%  filter(attackerTeam!=victimTeam) %>%  group_by(match_id,round_num) %>% summarise(map=last(map_name),T_team=last(if_else(attackerSide=="T","T","CT")))

most_played <- kills %>%  group_by(match_id ) %>%  summarize( attackerSteamID=last(attackerSteamID),attackerName=last(attackerName) ) %>% group_by(attackerSteamID) %>% summarize(name=last(attackerName),match_count=n())
most_played[order(most_played$match_count, decreasing=TRUE), ] %>% top_n(30)

wins <- kills %>%  filter(attackerTeam!=victimTeam) %>%  group_by(match_id,round_num) %>% summarise(map=last(map_name),winner=last(round_won_by),T_team=last(if_else(attackerSide=="T",attackerTeam,victimTeam)))

wins
```


```{r}


wins <- kills %>% group_by(match_id) %>% summarise(round_tot=last(round_tot)+1,team1=last(match_team1),team2=last(match_team2),winner=last(round_won_by),looser=if_else(last(round_won_by)!=last(match_team1),last(match_team1),last(team2)))

wins <- wins %>%  mutate(final_score_winner=if_else(round_tot<31,16, 19+3*(  (round_tot-31)%/%6))) %>%  mutate(final_score_looser=round_tot-final_score_winner) %>% mutate(score_diff=(final_score_winner-final_score_looser)/round_tot)
wins
               
kills
players <- kills %>% group_by(match_event,attackerSteamID)   %>%  summarise(name=last(attackerName),team=last(attackerTeam),date=last(match_date),event=last(match_event)  )
players
```



Team stats

kills

```{r}
#team stats on kills
team_kills <- kills %>% filter(attackerTeam!=victimTeam) %>%  group_by(match_id,attackerTeam) %>% summarise(kills_tot=n(),kpr=n()/last(round_tot),team=last(attackerTeam),hs_percent= sum(isHeadshot==TRUE)/n(),blinded_percent=sum(attackerBlinded==TRUE)/n(),blinded_percent=sum(victimBlinded==TRUE)/n(),first_kill_percent=sum(isFirstKill==TRUE)/last(round_tot),first_kill_percent=sum(isFirstKill==TRUE)/last(round_tot),non_traded_percent=sum(isTrade==FALSE)/n(),assist_percent= sum(!is.na(assisterTeam))/last(round_tot))

team_kills

#team stats on  damages
team_damages <- damages %>% filter(attackerTeam!=victimTeam) %>%  group_by(match_id,attackerTeam) %>% summarise(adr=sum(hpDamageTaken)/last(round_tot),team=last(attackerTeam),strafing=sum(attackerStrafe==TRUE)/n())

#team stat on flash 
flashes
team_flashes <- flashes %>% filter(attackerTeam!=playerTeam) %>%  group_by(match_id,attackerTeam) %>% summarise(avg_flash_duration=sum(flashDuration)/last(round_tot),team=last(attackerTeam))

#team stats for grenades
team_grenades <- grenades  %>% rename(attackerTeam=throwerTeam) %>%   group_by(match_id,attackerTeam) %>% summarise(grenades_per_round=n()/last(round_tot),team=last(attackerTeam),smokes_per_round=sum("Smoke Grenade"==grenadeType)/last(round_tot),attack_grenades_round=sum("Smoke Grenade"!=grenadeType)/last(round_tot),event=last(match_event))

#join everything
team_killsstat <- inner_join(team_kills,wins) %>% inner_join(team_damages) %>% inner_join(team_flashes) %>%  inner_join(team_grenades)  


#create y axis score difference data
team_killsstat <- team_killsstat %>% mutate(relative_score_diff=if_else(winner!=attackerTeam,-score_diff,score_diff))

```




PCA

```{r}

pca.variables <- c('kills_tot', 'kpr', 'hs_percent', 'blinded_percent', 'first_kill_percent',
'non_traded_percent', 'assist_percent', 'strafing', 'adr',  'avg_flash_duration', 'grenades_per_round')

team_killsstat.pca <- prcomp(team_killsstat[,pca.variables], center = TRUE,scale. = TRUE)

summary(team_killsstat.pca)

```


```{r}
library(cli)
library(devtools)
```


```{r}
install_github("vqv/ggbiplot")
```

```{r}
library(ggbiplot)

ggbiplot(team_killsstat.pca)
```

We now color points so that teams that have won appear in a certain color, and teams that didn't appear in another color.

```{r fig.height = 8}

p <- ggbiplot(team_killsstat.pca , obs.scale = 1, var.scale =1,circle=TRUE, groups=team_killsstat$win,varname.adjust = 1.6, varname.size = 2.5,  alpha = 0.7)
p <- p + xlim(-4.5, 3) + ylim(-3.1, 5)
p
```

