---
title: "R Notebook"
output: html_notebook
---

## data lion drive link: https://drive.google.com/drive/folders/10wndQSJ15Pvd97XwZ32J_BSu3F-clxIQ?usp=sharing


##Useful info for all rows

"round_won_by": team that won the round
 "match_id": "0 astralis-vs-cr4zy-m1-inferno" unique match identifier
"map_name": name of map played
 "round_num": number of the round from 1 to the last round
"round_tot": total number of rounds in the match
"match_event": unique event identifier ex "StarLadder Major Berlin 2019"
"match_date": date of match in milliseconds
"match_team1": name of a team
"match_team2": name of the other team


## This is how to load json files

```{r}
#This is how to load json files 
library(jsonlite)
kills <- jsonlite::fromJSON("data/ALL_kills.json", simplifyVector = TRUE)
```

## Example to get the average kill per round stat for each player (kpr)
```{r}
library(tidyverse)
head(kills)

#avg kills per match for each player (kpr = kill per round)
test <- kills %>% filter(attackerTeam!=victimTeam) %>%  group_by(match_id,attackerSteamID) %>% summarise(kpr=n()/last(round_tot),Name=last(attackerName))

#kpr over all matches
test <- test %>%  group_by(attackerSteamID) %>%  summarise(kpr=sum(kpr)/n(),tot_matches=n(),name=first(Name))
#Sort
test <- test %>% arrange( -kpr,-tot_matches)
test
```

## Example to get the average damage dealt per round stat for each player
```{r}
damages <- jsonlite::fromJSON("data/ALL_damages.json", simplifyVector = TRUE)
damages

#adr per match for each player
test <- damages %>% filter(attackerTeam!=victimTeam) %>%  group_by(match_id,attackerSteamID) %>% summarise(adr=sum(hpDamage)/last(round_tot),Name=last(attackerName))
#adr over all matches
test <- test %>%  group_by(attackerSteamID) %>%  summarise(adr=sum(adr)/n(),tot_matches=n(),name=first(Name))
#Sort
test <- test %>% arrange( -adr,-tot_matches)
test
```
K/D (Kills per Death)
```{r}
#kills per round
k <- kills %>% filter(attackerTeam!=victimTeam) %>%  group_by(match_id,attackerSteamID) %>% summarise(kills=n(),Name=last(attackerName))


k <- k %>%  group_by(attackerSteamID) %>%  summarise(kills=sum(kills),tot_matches=n(),name=first(Name))
#Sort
k <- k %>% arrange( -kills,-tot_matches)
k

#death per round
d <- kills %>% filter(attackerTeam!=victimTeam) %>%  group_by(match_id,victimSteamID) %>% summarise(deaths=n(),Name=last(victimName))


d <- d %>%  group_by(victimSteamID) %>%  summarise(deaths=sum(deaths),tot_matches=n(),name=first(Name))
#Sort
d <- d %>% arrange( deaths,-tot_matches)
d

joined <-  merge(k, d) %>% mutate(kd=kills/deaths)%>% mutate(kd_diff=kills-deaths) %>%  arrange( -kd,-tot_matches)
joined
```




# player id and name association (name vary over time so we have to use id (attackerSteamID) to refer to a player)
```{r}
steamid <- match  %>%  group_by(attackerSteamID) %>% summarise(Name=last(attackerName))
steamid
```


